---
title: "What can I do to make my next article (more) reproducible?"
author:
- name: Carlos Granell
  url: http://carlosgranell.eu
  affiliation: Universitat Jaume I
  affiliation_url: http://geotec.uji.es/
  orcid_id: 0000-0003-1004-9695
- name: Sergi Trilles
  url: http://www3.uji.es/~strilles/
  affiliation: Universitat Jaume I
  affiliation_url: http://geotec.uji.es/
  orcid_id: 0000-0002-9304-0719
  
date: "`r Sys.Date()`"
bibliography: references.bib
link-citations: true

description: |
  [UJI Doctoral School](https://www.uji.es/estudis/centres/escola-doctorat/base/info-general/escola/)'s cross-disciplinary training course on recommendations and best practices about reproducible research - [Academic year 2021/2022](https://www.uji.es/estudis/centres/escola-doctorat/base/arxiu/Formacio-transversal/21-22/recerca/).
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r meta, echo=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "cgranell/rrp-uji") %>%
  meta_social(
    title = "Reproducible Research Practices",
    url ="https://cgranell.github.io/rrp-uji/"
  )

```


This introductory course is currently scheduled to be offered in 2 or 3 weeks. While the course is running, some material might not be visible and will be unlocked as the course proceeds. At any other time, this website is continuously online, with small updates happening on an ongoing basis and larger updates every time the course is offered again.

## Course identification

**Code/Name**: MI007.TMP - Reproducible Research Practices

**Duration**: 6 hours (up to 20 hours including attendance and self-directed work)

**Dates**: 29 March, 5 and 11 April 2022, from 10 to 12

**Teaching language**: English (*Note: in Spanish even years, in English odd years*)

**Teaching staff**:

-   [Carlos Granell](http://geotec.uji.es/staff) <br> Associate Professor in Computer Science <br> Office [UB1520DD](http://smart.uji.es/index.php?room=UB1520DD), Espaitec2, 5th floor <br> Universitat Jaume I, Spain

-   [Sergi Trilles](http://geotec.uji.es/staff) <br> PostDoc - JdC <br> Office [UB-1518DD](http://smart.uji.es/index.php?room=UB1518DD), Espaitec2, 5th floor <br> Universitat Jaume I, Spain

Detail course description in [Spanish](https://ujiapps.uji.es/ade/rest/storage/HPOJUR5VMPQWDOCS6QGHUI6VX5LYWTDU) and  [English](https://ujiapps.uji.es/ade/rest/storage/Z8KFWYOHSZYNTH6WKH0DRGQVLCPLCM8P)


## Purpose 

This course emphasises the principles and strategies of open science and reproducible research practices and gives you practice in their application to present scientific and technical material in an informative and clear manner.

<aside>

We are not talking about “learning to programme” as a course objetive or "knowing how to
programme” as a previous requirement. Of course, an open mindset is presupposed so that the course participants can incorporate new practices/recommendations into their research process.

</aside>

## Learning outcomes

Briefly, the course's learning outcomes are to help you:

-   [RRP01] Recognise the importance of (computational) reproducible research as a fundamental pillar of modern science.
-   [RRP02] Compare and contrast the RE-* terms (reproduce, replicate, recreate, etc) within the context of each participant's own discipline.
-   [RRP03] Describe and distinguish the reproducibility criteria.
-   [RRP04] Assess participants' own work according to the reproducibility criteria.
-   [RRP05] Organise a research project to facilitate reproducibility, openness and reuse.
-   [RRP06] Contrast the main families of licences for software and data.
-   [RRP07] Understand the value of combining questions, source code and outcomes.
-   [RRP08] Apply notebooks to the documentation of computational analyses.
-   [RRP09] Design and create notebooks for producing academic articles, technical reports or presentations.
-   [RRP09] Create a **Reproduction Plan** and reflect on the next steps to achieve it.



## Getting started

This web site is the main `theatre entrance` to the `play` of reproducible  research practices, and participants, you all, are the main `performers`! To start, click on `casting` to get general information about the course, such as the [code of conduct](code_of_conduct.html), [`roles` in the play](personas.html) (or learning persona) and the [`acts`](schedule.html) (or course schedule). Tonight's `play`, with `acts` and `scenes`, is ready to be performed on the `stage`. If you like it, feel free to go `backstage` to inspect additional documents and materials to go deeper into this topic. If you *really, really* love the topic (and read Spanish), meet the [`crew`](blog.html) behind the `curtain`.


## Acknowledgements

This course was developed and is maintained by [Carlos Granell](http://carlosgranell.eu).

The following individuals have contributed to improving the course: ...

The course materials are licensed under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-nc-sa/4.0/). Linked materials are governed by their own licenses. I assume that all external materials used here are covered under the educational fair use policy. If this is not the case and any material displayed here violates copyright, please let me know and I will remove it.

