---
title: "Act II &#183; Recommendations and practices for open and reproducible research"
description: |
  Scene 3 &#183; After: writing and sharing reproducible resources
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning outcomes...

-   [RRP05] **Organise** a research project to facilitate reproducibility, openness and reuse.

-   [RRP06] **Contrast** the main families of licences for software and data.


## Content...

-   We discuss practices and recommendations to get started with reproducibility

-   We introduce and compare types of licences


## Organisation & materials

**[Estimated time: 4 hours]**

1.    ["After: writing and sharing reproducible resources" (slides)](slides/slides23_01.html) summarises some of the organizational aspects and reproducible practices for the preparation and first steps of a project.

```{r embed-again, echo=FALSE, fig.cap="[Slides](slides/slides23_01.html)"}
  xaringanExtra::embed_xaringan(url = "slides/slides23_01.html#title", ratio = "16:9")
```




## Assignments


