---
title: "Act I &#183; Setting the stage"
description: |
  Scene 2 &#183; Reproducibility criteria
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  Learning outcomes...

-   [RRP03] **Describe and distinguish** the reproducibility criteria.

-   [RRP04] **Assess** the reproducibility criteria in the student's own research papers or scientific writings.

## Content...

-   We identify resources that are part of the scientific process, beyond the published scientific article.

-   We characterise these resources according to reproducibility criteria.

-   We use and interpret correctly the levels associated with each criterion.

-   We discuss the role of Open Science and reproduction in a PhD project.


## Organisation & materials

**[Estimated time: 2 hours]**

1.  To get some context on how reproducibility and [Open Science](glossary.html#open-science) fit into your research process and practices: "[PhD thesis meets reproducibility" (slides)](slides/slides12_01.html). <!--y [video](https://drive.google.com/file/d/1mtSO0BrrvlCMEN7LBXQaa7dIGYMGgsOw/view?usp=sharing).-->

    ```{r embed-again, echo=FALSE, fig.cap="[Slides](slides/slides12_01.html)"}
    xaringanExtra::embed_xaringan(url = "slides/slides12_01.html#title", ratio = "16:9")
    ```

2.  Read the first three sections (*Introduction, Related Work, Materials & Methods*) of the following paper [@nust2018], where a set of criteria are proposed to evaluate the degree of reproducibility of an article. (If motivated, you can also read the section 3.1 of the paper [@ostermann2021].) Pay attention to [figure 2](https://doi.org/10.7717/peerj.5072/fig-2), which outlines the levels for each of the reproducibility criteria. You should familiarise yourself with these criteria and their levels to carry out the first activity of the *Reproduction Plan*.

<!--
3.  Reflexiona sobre tu proceso y prácticas de investigación en general (no te focalices en un proyecto o artículo en concreto) y contesta a las siguientes preguntas.

    -   Indica departamento y/o grupo de investigación.

    -   ¿Realizas una investigación teórica-conceptual, práctica-experimental, o una combinación de ellas?

    -   ¿Juegan los datos de entrada un papel importante en tu investigación? ¿Utilizas fuentes de datos ya existentes? ¿O generas los datos expresamente para tu investigación (p.e. cuestionarios)?

    -   ¿Necesitas ajustar, arreglar, limpiar, en definitiva, pre-procesar los datos de entrada para tu investigación?

    -   ¿Realizas algún análisis o aplicas algún modelo sobre los datos? ¿Utilizas alguna herramienta tecnológica ya existente para el análisis, o escribes tu propio código para analizar los datos? ¿O ambas cosas?

    -   ¿Las tablas, figuras, gráficos, mapas o diagramas son resultados habituales en tu investigación, es decir, aparecen frecuentemente en tus informes o artículos finales?
-->

## Assignments

-   To begin with the *Reproduction Plan*, choose one of your recent published paper or a current draft, and carry out a self-assessment exercise in which you must assign a level (NA *Not Applicable*, 0 *Unavailable*, 1 *Documented*, 2 *Available*, 3 *Available and Open*) for each of the reproducibility criteria: Input Data; Preprocessing; Methods, Analysis, Processing; Computational Environment; Results.
  
  
<!-- this goes to ACt II 
Reflect on those reproducibility criteria that are most difficult for you to carry out (for example, due to lack of technical knowledge or support tool or simply because you have never taken them into account). Highlight three aspects (maximum) that you would like to try to improve for the next research article. -->
   
