---
title: "Act I &#183; Setting the stage"
description: |
  Scene 1 &#183; Reproducibility and replicability
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Learning outcomes...**


-   [RRP01] **Recognise** the importance of (computational) reproducible research as a fundamental pillar of modern science.

-   [RRP02] **Compare and contrast** the RE-* terms (reproduce, replicate, recreate, etc) within the context of each participant's own discipline.


## **Content...**

-   We recognize the importance of reproduction and replication as part of the scientific method and open science.

-   We introduce the concepts of reproducibility and replicability.

-   We compare reproduction practices and standards required/perceived in different disciplines or areas of knowledge.


## Activities & materials

**[Estimated time: 2 hours]**

1.  Of the examples of [Learner Personas](personas.html), with which one do you identify the most, even if it doesn't quite fit your profile?

2.  Review the concepts of reproducibility, replication, and computational reproducibility in [Reproducibility: historical notes & concept (slides)](slides/slides11_01.html) <!--and [video](https://drive.google.com/file/d/1Fjd37NPEINIRgCOdmaa892ayG2IRaV7H/view?usp=sharing)-->.

    ```{r embed-again, echo=FALSE, fig.cap="[Slides](slides/slides11_01.html)"}
    xaringanExtra::embed_xaringan(url = "slides/slides11_01.html", ratio = "16:9")
    ```

3.  Reflexiona en qué medida estos términos (reproducción, replicación) están extendido en tu propia disciplina o área de investigación. ¿Cuál es más predominante en tu disciplina? ¿Qué incluyen colegas de disciplina en sus artículos para que sean reproducibles y/o replicables? De las revistas en las que publicas, ¿solicitan artículos reproducibles?

4.  Reflexiona en qué grado tienes en cuenta el enfoque predominante en cuanto a reproducibilidad/replicabilidad de tu disciplina en tus propias investigaciones pasadas/presentes?

5.  (Opcional) Si aún dudas en abrazar la reproducibilidad, [Five Selfish Reasons to Work Reproducibly by Dr. Florian Markowetz](https://www.youtube.com/watch?v=yVT07Sukv9Q)], basado en su publicación homónima [@markowetz2015], te convencerá.

## **Entrega**

-   Indicate the [Learner Persona](personas.html) with whom you best identify (activity 1) in the **Learner Persona Survey** in the AV.

-   Sube tu auto-reflexión (actividades 3 y 4) en el foro **Auto-reflexión sobre reproducibilidad/replicabilidad de tu disciplina** en el Aula Virtual e indica también la disciplina a la que perteneces en el mensaje.
