---
title: "Act I &#183; Setting the stage"
description: |
  Scene 2 &#183; PhD meets open science
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  Learning outcomes...

-   [RRP01] **Recognise** the importance of (computational) reproducible research as a fundamental pillar of open science.

## Content...

-   We identify resources that are part of the scientific process, beyond the published scientific article.

-   We discuss the role of Open Science and reproduction in a PhD project.


## Organisation & materials

**[Estimated time: 2 hours]**

1.  To get some context on how reproducibility and [Open Science](glossary.html#open-science) fit into your research process and practices: "[Open, reproducible, and replicable (PhD) research" (slides)](slides/slides12_01.html). <!--y [video](https://drive.google.com/file/d/1mtSO0BrrvlCMEN7LBXQaa7dIGYMGgsOw/view?usp=sharing).-->

    ```{r embed-again, echo=FALSE, fig.cap="[Slides](slides/slides12_01.html)"}
    xaringanExtra::embed_xaringan(url = "slides/slides12_01.html#title", ratio = "16:9")
    ```

2. Reflect on your research process and practices in general (do not focus on a specific project or article) and answer the following questions.

-   Indicates department and/or research group.

-   Do you carry out theoretical-conceptual, practical-experimental research, or a combination of them?

-   Does input data play an important role in your research? Do you use existing data sources? Or do you generate the data expressly for your research (eg questionnaires)?

-   Do you need to adjust, fix, clean, aggregate, that is, pre-process input data for your research?

-   Do you carry out any analysis or apply any model on the data? Do you use any existing technology tools for analysis, or do you write your own code to analyse the data? Or both?

-   Are the tables, figures, graphs, maps or diagrams common results in your research, that is, do they frequently appear in your final reports or articles?

## Assignments

-   Answer the questions posed in Activity 2 above to the corresponding activity in AV.
  
