---
title: "Act I &#183; Setting the stage"
description: |
  Scene 1 &#183; Reproducibility and replicability
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning outcomes...

-   [RRP01] **Recognise** the importance of (computational) reproducible research as a fundamental pillar of modern science.

-   [RRP02] **Compare and contrast** the {Re}* terms (reproduce, replicate, recreate, etc) within the context of each participant’s own discipline.

## Content...

-   We recognize the importance of reproduction and replication as part of the scientific method and open science.

-   We introduce the concepts of reproducibility and replicability.

-   We compare reproduction practices and standards required/perceived in different disciplines or areas of knowledge.


## Organisation & materials

**[Estimated time: 2 hours]**

0.  Who are we? A [brief historical account](https://docs.google.com/presentation/d/14zJk4Rx0JIFIEbF6qy_V1Pi17z0zafbrh9sZxotK0RQ/edit?usp=sharing) of [reproducibility](glossary.html#reproducibility) in the [AGILE conference series](https://agile-online.org/). Check out [Reproducible Research @ AGILE](https://reproducible-agile.github.io/)

1.  Of the examples of [Learner Personas](personas.html), with which one do you identify the most, even if it doesn't quite fit your profile?

2.  Review the concepts of reproducibility, replication, and computational reproducibility in [Reproducibility: historical notes & concept (slides)](slides/slides11_01.html) <!--and [video](https://drive.google.com/file/d/1Fjd37NPEINIRgCOdmaa892ayG2IRaV7H/view?usp=sharing)-->.

    ```{r embed-again, echo=FALSE, fig.cap="[Slides](slides/slides11_01.html)"}
    xaringanExtra::embed_xaringan(url = "slides/slides11_01.html#title", ratio = "16:9")
    ```

3.  Reflect on the extent to which these terms ([reproduction, replication, robustness, generalisation](slides/slides11_01.html#matrix_definitions)) are widespread in your own discipline or area of research. Which is more predominant in your discipline? And in your research? Of the journals you publish or flag-ship journals in your discipline, do they request articles that support computational reproducibility, empirical reproducibility, or statistical reproducibility? (*hint*: check The Turing Way's [definitions page](https://the-turing-way.netlify.app/reproducible-research/overview/overview-definitions.html) [@turingway2019]).


4.  (Optional) If you're still hesitant to embrace reproducibility, [Five Selfish Reasons to Work Reproducibly by Dr. Florian Markowetz](https://www.youtube.com/watch?v=yVT07Sukv9Q)], based on his paper [@markowetz2015], will convince you!

## Assignments

-   Indicate the [Learner Persona](personas.html) with whom you best identify (activity 1) in the **Learner Persona Survey** in AV.

-   Write a message (min 150 words) to answer the questions posed in Activity 3 above to the forum  **Reflection on reproducibility/replicability in your discipline and in your own research** in AV. Please, indicate in the message your discipline or area of knowledge.
