---
title: "After analysis &#183; writing and sharing reproducible resources"
subtitle: "[Act II] Recomendations and practices for open and reproducible research"
author: "Carlos Granell"
institute: "Universitat Jaume I"
date: "April 2022"
description: "Reproducible Research Practices (RRP'23)"
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css", "custom.css"]
    seal: false
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
      ratio: "16:9"
---
name: title
class: Left, middle


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
# knitr::opts_chunk$set(collapse = TRUE,
#                       fig.retina = 3)

knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)


```

```{r xaringan-extra, echo=FALSE}
library(xaringanExtra)

xaringanExtra:::use_xaringan_extra(c("tile_view", "panelset", "share_again", "editable"))

xaringanExtra::style_share_again(
  share_buttons = c("twitter", "linkedin", "pocket"))
xaringanExtra::use_scribble(
  pen_color = "#d33f49", pen_size = 4)
```


```{r xaringan-themer, include=FALSE, warning=FALSE}
source("xaringan-themer.R")
```

```{r, load_refs, include=FALSE, cache=FALSE}
source("load_references.r")
```


```{r load, echo=FALSE}
library(report)
```

# `r rmarkdown::metadata$title`

### `r rmarkdown::metadata$subtitle`

.large[`r rmarkdown::metadata$description` &#183; `r rmarkdown::metadata$date`]

.right[`r rmarkdown::metadata$author` &#183; Sergi Trilles]

.right[`r rmarkdown::metadata$institute`]


---
class: inverse, bottom, middle

## Karl Pooper's *Conjectures and Refutations*

.large[The ideas we can most trust are those that have been the most tried and tested]

???

[Karl Popper](https://en.wikipedia.org/wiki/Karl_Popper)

---
name: rec21
class: inverse, center, middle

# .blue.bg-white[\#21]

# Avoid *Data (or code) available upon request*

---
class: left
### Data (or code) available upon request

.huge[`r cite("stodden2018")` -  `r title("stodden2018")`]

.large[...only .gray.bg-blue[44%] of requests led to receiving data and/or code from the original authors]



---
name: rec22
class: inverse, center, middle

# .blue.bg-white[\#22]

# Report the software version you use

---
class: left, top
### Software version

.huge[Specify versions of relevant software components (packages, libraries)]

.huge[A different version can lead to different results!]

.large[`r cite("mesnard2017")` - `r title("mesnard2017")`]

-   .large[Check "Story 4: Different Versions of Code, External Libraries, or Compilers can Challenge Reproducibility"]

---
name: rec23
class: inverse, center, middle

# .blue.bg-white[\#23]

# Cite the software you use


---
class: left
### Software citation

.huge[Cite software that's important to the research outcome]

-   .large[[R engine](https://ropensci.org/blog/2021/11/16/how-to-cite-r-and-r-packages/)?] 

  - type  `citation()` to get reference publication in bibtex entry
  - add "All analyses were performed using R Statistical Software (v4.2.2; R Core Team 2022)" to **DASA section**

-   .large[[R packages](https://ropensci.org/blog/2021/11/16/how-to-cite-r-and-r-packages/)? It depends...]

  - type `citation("<packageName>")` to get reference publication in bibtex format 
  - add "Temperature data was obtained from Environment and Climate Change Canada via the `weathercan` R package (v0.6.2; LaZerte and Albers 2018)" to **DASA section**.



---
class: left
### Software citation

.huge[[`report`](https://cran.r-project.org/package=report) R Package]

```{r}
report::report_system()
```

```{r}
report::report_packages()
```


---
class: left
### Software citation

.pull-left[

.huge[Do not use URL to cite external library/code/software]

-   .large[Cite `SciPy` as a footnote: https://scipy.org/?]

]

--

.pull-right[

.huge[Cite software as any other paper instead] 

-   .large[Cite `SciPy` as a paper: [Virtanen et al. (2020)](https://scholar.google.com/scholar?hl=en&as_sdt=0%2C5&q=SciPy+1.0%3A+fundamental+algorithms+for+scientific+computing+in+Python&btnG=)?]

]

--

.huge[Readings:]

-   .large[[Software Citation Checklist for Authors](https://zenodo.org/record/3479199#.YYmfT73MKAk)]

-   .large[`r title("smith2016")` `r cite("smith2016")`]


---
name: rec24
class: inverse, center, middle

# .blue.bg-white[\#24]

# Hello Quarto (and friends)

---
class: left
### Hello Quarto (and friends)

Truly reproducible figures and tables are created directly with code and integrated into documents in a way that allows automatic updating when analyses are re-run, creating a “dynamic” document



---
name: rec25
class: inverse, center, middle

# .blue.bg-white[\#25]

# Pre-print your work 

---
class: left
### Preprints

To increase access to publications, authors can post preprints of final (but preacceptance) versions of manuscripts on a preprint server, or postprints of manuscripts on postprint servers.


---
name: rec26:
class: inverse, center, middle

# .blue.bg-white[\#26]

# Research Compendia

---
class: left
### Research Compendia

- When data, code, software, and products of a research project are archived together, these are termed a “research compendium"

- They provide a standardized and easily recognizable way to organize the digital materials of a research project, which enables other researchers to inspect, reproduce, and extend research

-  Open Science Framework (OSF; http://osf.io/. The goal of the OSF is to enable research to be shared at every step of the scientific process—from developing a research idea and designing a study, to storing and analyzing collected data and writing and publishing reports or papers 

Sullivan, I., A. DeHaven, and D. Mellor. 2019. Open and reproducible research on Open Science Framework. Current Protocols Essential Laboratory Techniques 18:e32.

-   [Octopus and ResearchEquals aim to break the publishing mould](https://www.nature.com/articles/d41586-023-00861-0)


---
name: rec27
class: inverse, center, middle

# .blue.bg-white[\#26]

# Interactive papers


---
class: left
### Interactive papers

[Advancing Reproducible Research by Publishing R Markdown Notebooks as Interactive Sandboxes Using the learnr Package](https://journal.r-project.org/articles/RJ-2022-021/) `r cite("tso2022")`


---
name: summary
class: inverse, center, middle

# Summary

---

-    .large[[Avoid *Data (or code) available upon request*](#rec21)]

-    .large[[Report the software version you use](#rec22)]

-    .large[[Cite the software you use](#rec23)]

-    .large[[Hello Quarto (and friends)](#rec24)]

-    .large[[Pre-print your work](#rec25)]

-    .large[[Research Compendia](#rec26)]

-    .large[[Interactive papes](#rec27)]



---

# References

.tiny[
```{r print_refs1, echo=FALSE, results="asis"}
print(start = 1, end = 4)
```
]

