---
title: "Advanced recommendations for open and reproducible research"
subtitle: "[2.1] Recomendations and practices"
author: "Carlos Granell"
institute: "Universitat Jaume I"
date: "March 2022"
description: "Reproducible Research Practices (RRP'23)"
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css", "custom.css"]
    seal: false
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
      ratio: "16:9"
---
name: title
class: Left, middle


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
# knitr::opts_chunk$set(collapse = TRUE,
#                       fig.retina = 3)

knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)


```

```{r xaringan-extra, echo=FALSE}
library(xaringanExtra)

xaringanExtra:::use_xaringan_extra(c("tile_view", "panelset", "share_again", "editable"))

xaringanExtra::style_share_again(
  share_buttons = c("twitter", "linkedin", "pocket"))
xaringanExtra::use_scribble(
  pen_color = "#d33f49", pen_size = 4)
```


```{r xaringan-themer, include=FALSE, warning=FALSE}
source("xaringan-themer.R")
```

```{r, load_refs, include=FALSE, cache=FALSE}
source("load_references.r")
```


# `r rmarkdown::metadata$title`

### `r rmarkdown::metadata$subtitle`

.large[`r rmarkdown::metadata$description` &#183; `r rmarkdown::metadata$date`]

.right[`r rmarkdown::metadata$author` &#183; Sergi Trilles]

.right[`r rmarkdown::metadata$institute`]


---
class: inverse, bottom, middle

## Karl Pooper's *Conjectures and Refutations*

.large["At the core of the scientific method is the attempt to refute or disprove theories"]

???

[Karl Popper](https://en.wikipedia.org/wiki/Karl_Popper)


---
class: left

##  What is the scientific method? (for Popper)

.huge[Science progresses through *conjectures and refutations*]

--

-   .large[Scientists are confronted with some question, and offer a possible answer] 

--

-   .large[The  answer is a *conjecture* initially (is it right or wrong?)]

--

-   .large[Scientists do their best to *refute* this conjecture, or prove it wrong]

--

-   .large[Typically it is refuted, rejected, and replaced by a better one]

--

-   .large[This too will then be tested, and eventually replaced by an even better one]

--

-   .large[If scientists have not been able to refute a theory over a long period of time, despite their best efforts, then the theory has been *corroborated*]


???

Source: [Why should we trust science? Because it doesn’t trust itself](https://theconversation.com/why-should-we-trust-science-because-it-doesnt-trust-itself-188988)


---
class: inverse, bottom, middle

## Karl Pooper's *Conjectures and Refutations*

.large[The ideas we can most trust are those that have been the most tried and tested]

???

[Karl Popper](https://en.wikipedia.org/wiki/Karl_Popper)



---
name: a1
class: inverse, center, middle

# .blue.bg-white[\#1]

# Be (data) FAIR, my friend

---
class: left
### (Data) FAIR 

.huge[[Findable, Accesible, Interoperable, Reusable](https://www.go-fair.org/fair-principles/) for scientific data management and stewardship]

-   .large[Emphasis on data & metadata documentation]

-   .large[[How to GO FAIR](https://www.go-fair.org/how-to-go-fair/)]

<br/>

.large[**[What UJI recommends...](http://www.uji.es/upo/rest/contenido/630998650/raw?idioma=es)**]

---
class: left
### Be (data) FAIR, my friend

https://ieeexplore.ieee.org/document/8816763


---
name: a2
class: inverse, center, middle

# .blue.bg-white[\#2]

# Use open source software whenever possible

---
class: left
### Open source software

Use open source software instead of commercial software

---
name: a3
class: inverse, center, middle

# .blue.bg-white[\#3]

# Learn/use scripting languages 

---
class: left
### Scripting languages 

https://ieeexplore.ieee.org/document/9153295

Play with numbers, measure & explore data, distrust of your intuition


---
name: a4
class: inverse, center, middle

# .blue.bg-white[\#4]

# Learn/use computational notebook formats

---
class:left 
### Computational notebook formats

jupyter, rmarkdown, quarto


---
name: a5
class: inverse, center, middle

# .blue.bg-white[\#5]

# Learn/use version control systems


---
class: left
### Version control systems

.huge[Turn you project folder into a local version control repository]

-   .large[to keep track changes of your work]

-   .large[to provide a complete historical log of your project]

-   .large[to handle properly text formats (code, text documents, markdown documents) as opposed to rich/binary formats (Word)] 

---
class: left
### Version control systems
  
.huge[Tools]: 

-   .large[SVN, Mercurial, [Git](https://git-scm.com/)]

.huge[Readings]: 

-   .large[[Getting started with git](https://git-scm.com/book/en/v2/Getting-Started-Installing-Git)]
-   .large[[An introduction to Git: what it is, and how to use it](https://www.freecodecamp.org/news/what-is-git-and-how-to-use-it-c341b049ae61/)]
-   .large[`r cite("perez2016")`, `r cite("bryan2020")`]

---
name: a6
class: inverse, center, middle

# .blue.bg-white[\#6]

# Use online (Git) repository hosting services

---
class: left
### Online (Git) repository hosting services

.huge[Easier for individuals and teams to use Git for version control and collaboration]

-   .large[VCS + collaborative features + development support features]

.huge[Tools]: .large[[GitLab](https://about.gitlab.com/), [Bitbucket](https://bitbucket.org/), [GitHub](https://github.com/)]

.huge[Readings]: 

-   .large[[Cookiecutter Data Science: Best practices for organising your repository for easy version control](https://drivendata.github.io/cookiecutter-data-science/)]

-   .large[`r cite("perez2016")`, `r cite("bryan2020")`]

---
name: a6
class: inverse, center, middle

# .blue.bg-white[\#6]

# Learn/use containerisation tools


---
class: left
### Containerisation tools


---
name: a6
class: inverse, center, middle

# .blue.bg-white[\#6]

# Be (software) FAIR, my friend

---
class: left
### (Software) FAIR

https://www.nature.com/articles/s41597-022-01710-x


---
name: a6
class: inverse, center, middle

# .blue.bg-white[\#6]

# Make use of *Make*


---
name: summary
class: inverse, center, middle

# Summary

---

1.    .large[Be (data) FAIR, my friend]

1.    .large[Use open source software whenever possible]

1.    .large[Learn/use scripting languages]

1.    .large[Learn/use computational notebook formats]

1.    .large[Learn/use version control (Git)]

1.    .large[Use online repository hosting services]

1.    .large[Learn/use containerisation tools]

1.    .large[Be (software) FAIR, my friend]

1.    .large[Make use of *Make*]


---

# References

.tiny[
```{r print_refs1, echo=FALSE, results="asis"}
print(start = 1, end = 4)
```
]

