---
title: "Advanced recommendations for reproducible projects"
subtitle: "[2.1] Recomendations and practices"
author: "Carlos Granell"
institute: "Universitat Jaume I"
date: "April 2022"
description: "Reproducible Research Practices (RRP'22)"
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css", "custom.css"]
    seal: false
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
      ratio: "16:9"
---
name: title
class: Left, middle


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
# knitr::opts_chunk$set(collapse = TRUE,
#                       fig.retina = 3)

knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)


```

```{r xaringan-extra, echo=FALSE}
library(xaringanExtra)

xaringanExtra:::use_xaringan_extra(c("tile_view", "panelset", "share_again", "editable"))

xaringanExtra::style_share_again(
  share_buttons = c("twitter", "linkedin", "pocket"))
xaringanExtra::use_scribble(
  pen_color = "#d33f49", pen_size = 4)
```


```{r xaringan-themer, include=FALSE, warning=FALSE}
source("xaringan-themer.R")
```

```{r, load_refs, include=FALSE, cache=FALSE}
source("load_references.r")
```


# `r rmarkdown::metadata$title`

### `r rmarkdown::metadata$subtitle`

.large[`r rmarkdown::metadata$description` &#183; `r rmarkdown::metadata$date`]

.right[`r rmarkdown::metadata$author` &#183; Sergi Trilles]

.right[`r rmarkdown::metadata$institute`]



---
class: center, middle

# Use Version Control Systems (VCS)


---

# .center[Version Control Systems] 

.pull-left[

### Turn you project folder into a local version control repository

- to keep track changes of your work

- to provide a complete historical log of your project 

- to handle properly text formats (code, text documents, markdown documents) as opposed to rich/binary formats (Word). 
  
]

.pull-right[
### Tools: 

- SVN, Mercurial, [Git](https://git-scm.com/)

### Additional readings: 

- [Getting started with git](https://git-scm.com/book/en/v2/Getting-Started-Installing-Git)

- [An introduction to Git: what it is, and how to use it](https://www.freecodecamp.org/news/what-is-git-and-how-to-use-it-c341b049ae61/) 

- `r cite("perez2016")`, `r cite("bryan2020")`

]

---
class: center, middle

# Use online code repositories services

---

# .center[Online code repositories services] 

.pull-left[

### Web-based platform for hosting code repositories

- VCS + collaborative features

]

.pull-right[
### Tools: 

- [GitLab](https://about.gitlab.com/), [Bitbucket](https://bitbucket.org/), [GitHub](https://github.com/)

### Additional readings: 

- [Cookiecutter Data Science: Best practices for organising your repository for easy version control](https://drivendata.github.io/cookiecutter-data-science/)

- `r cite("perez2016")`, `r cite("bryan2020")`

]

---

# Summary


---

# References

.tiny[
```{r print_refs1, echo=FALSE, results="asis"}
print(start = 1, end = 4)
```
]

